# Child wasting and underweight stratified by low birthweight and preterm birth status {#BWstrat}

---
output:
  pdf_document:
    keep_tex: yes
fontfamily: mathpazo
fontsize: 9pt
---

\raggedright




```{r setup1, include=FALSE}
source(paste0(here::here(), "/0-config.R"))
library(knitr)
library(DT)
knitr::opts_chunk$set(echo = TRUE)


load(paste0(fig_dir,"underweight/figure-data/BW_strat_figs.Rdata"))
load(paste0(fig_dir,"underweight/figure-data/BW_strat_tabs.Rdata"))

```

## Weight-for-age Z-score (WAZ)


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
plot_birthwt
```

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
plot_gagebrth
```

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
plot_birthwt.gagebrth
```

## Weight-for-length Z-score (WLZ)


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
plot_birthwt_wlz
```

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
plot_gagebrth_wlz
```

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
plot_birthwt.gagebrth_wlz
```

## Age-specific prevalence of wasting, stratified by birthweight

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight_wast$plot
```

## Age-specific prevalence of wasting, stratified by gestational age


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_gagebrth_wast$plot
```


## Age-specific prevalence of wasting, stratified by birthweight and gestational age

#### Overall

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight_gagebrth_overall_wast$plot
```

#### African cohorts

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight_gagebrth_africa_wast$plot
```

#### South Asian cohorts

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight_gagebrth_asia_wast$plot
```



## Age-specific prevalence of underweight, stratified by birthweight

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight$plot
```

## Age-specific prevalence of underweight, stratified by gestational age


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_gagebrth$plot
```


## Age-specific prevalence of underweight, stratified by birthweight and gestational age

#### Overall

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight_gagebrth_overall$plot
```

#### African cohorts

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight_gagebrth_africa$plot
```

#### South Asian cohorts

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 6.5}
prev_plot_birthweight_gagebrth_asia$plot
```


## Tables

```{r, echo=F, warning=F, message=F}
DT::datatable(tab_birthweight)
```

```{r, echo=F, warning=F, message=F}
DT::datatable(tab_gagebrth)
```

```{r, echo=F, warning=F, message=F}
DT::datatable(tab_birthwt_gagebrth)
```



