# Tabulation of low birthweight and preterm birth status among children ever wasted or underweight in the first 6 months of life. {#ciBWstrat}

---
output:
  pdf_document:
    keep_tex: yes
fontfamily: mathpazo
fontsize: 9pt
---

\raggedright




```{r setup1, include=FALSE}
source(paste0(here::here(), "/0-config.R"))
library(knitr)
library(kableExtra)
#library(DT)
knitr::opts_chunk$set(echo = TRUE)


load(paste0(fig_dir,"underweight/figure-data/Uwt_u6_strat_tabs.Rdata"))

```

This page contains tables of birthweight and gestational age status among children wasted or underweight in the first 6 months of life. Note this includes children who were born wasted or underweight.

## Overall tabulation of birthweight and gestational age status 

These tables include all children (including children not wasted or underweight in the first 6 months)

### Birthweight - all cohorts

```{r, echo=F, warning=F, message=F}
overall$overall$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - all monthly measured cohorts

```{r, echo=F, warning=F, message=F}
overall_monthly$overall$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - African cohorts

```{r, echo=F, warning=F, message=F}
overall$africa$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - African monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
overall_monthly$africa$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - South Asian cohorts

```{r, echo=F, warning=F, message=F}
overall$asia$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - South Asian monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
overall_monthly$asia$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```


### Gestational age - all cohorts

```{r, echo=F, warning=F, message=F}
overall$overall$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - all monthly measured cohorts

```{r, echo=F, warning=F, message=F}
overall_monthly$overall$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - African cohorts

```{r, echo=F, warning=F, message=F}
overall$africa$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - African monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
overall_monthly$africa$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - South Asian cohorts

```{r, echo=F, warning=F, message=F}
overall$asia$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - South Asian monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
overall_monthly$asia$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```



## Tabulation of birthweight and gestational age status among children wasted in the first 6 months of life

These tables include only children with any wasting measurement (WLZ < -2) in the first 6 months of life.

### Birthweight - all cohorts

```{r, echo=F, warning=F, message=F}
wasting$overall$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - all monthly measured cohorts

```{r, echo=F, warning=F, message=F}
wasting_monthly$overall$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - African cohorts

```{r, echo=F, warning=F, message=F}
wasting$africa$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - African monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
wasting_monthly$africa$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - South Asian cohorts

```{r, echo=F, warning=F, message=F}
wasting$asia$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - South Asian monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
wasting_monthly$asia$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```


### Gestational age - all cohorts

```{r, echo=F, warning=F, message=F}
wasting$overall$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - all monthly measured cohorts

```{r, echo=F, warning=F, message=F}
wasting_monthly$overall$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - African cohorts

```{r, echo=F, warning=F, message=F}
wasting$africa$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - African monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
wasting_monthly$africa$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - South Asian cohorts

```{r, echo=F, warning=F, message=F}
wasting$asia$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - South Asian monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
wasting_monthly$asia$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```









## Tabulation of birthweight and gestational age status among children underweight in the first 6 months of life

These tables include only children with any underweight measurement (WAZ < -2) in the first 6 months of life.

### Birthweight - all cohorts

```{r, echo=F, warning=F, message=F}
underweight$overall$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - all monthly measured cohorts

```{r, echo=F, warning=F, message=F}
underweight_monthly$overall$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - African cohorts

```{r, echo=F, warning=F, message=F}
underweight$africa$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - African monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
underweight_monthly$africa$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - South Asian cohorts

```{r, echo=F, warning=F, message=F}
underweight$asia$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Birthweight - South Asian monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
underweight_monthly$asia$tab_birthwt %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```


### Gestational age - all cohorts

```{r, echo=F, warning=F, message=F}
underweight$overall$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - all monthly measured cohorts

```{r, echo=F, warning=F, message=F}
underweight_monthly$overall$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - African cohorts

```{r, echo=F, warning=F, message=F}
underweight$africa$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - African monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
underweight_monthly$africa$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - South Asian cohorts

```{r, echo=F, warning=F, message=F}
underweight$asia$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```

### Gestational age - South Asian monthly-measured cohorts

```{r, echo=F, warning=F, message=F}
underweight_monthly$asia$tab_gagebrth %>%
  kable("html") %>%
  kable_styling(font_size = 14)
```





